\documentclass[11pt,article,oneside]{memoir}
\usepackage{org-preamble-xelatex}

\usepackage{url}

\date{}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Michael Steeves}
\def\mytitle{Resume}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myemail{msteeves@pair.com}
\def\myphone{Available Upon Request}
\def\myversion{}
\def\myrevision{}

\def\mykeywords{Michael, Steeves, Michael Steeves, CV, Resume,
  Bioinformatics, IT, HPC}

%%%------------------------------------------------------------------------
%%% Git version tracking
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
\input{vc}

\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe.
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text},
        Numbers={OldStyle},
        Ligatures={Common}]{Minion Pro}
%%\setsansfont[Mapping=tex-text,
%%        Ligatures={Common},
%%        Colour=AA0000]{Unit-Medium}
%%\setmonofont[Mapping=tex-text,Scale=0.72]{PragmataPro}

\newfontface\scheader[SmallCapsFont={Minion Pro},SmallCapsFeatures={Letters=SmallCaps}]{Minion Pro}

\newfontface\addressblock[Mapping={tex-text},
        Numbers={OldStyle},
        Ligatures={Common}]{Minion Pro}

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\textsf{{\footnotesize\vspace{-1em}\flushright #1}}}}


%% [optional] custom ampersand (font consistent with the one chosen above)
% \newcommand{\amper}{{\fontspec[Scale=.95,Colour=AA0000]{Minion Pro Medium}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~}

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------

% These lines will insert git revision info in the footer, using the vc
% package---see docs for vc package for details. Comment out this line
% if you're not using vc, and also remove the \input{vc} line above.
\pagestyle{kjh}
\thispagestyle{kjhgit}

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize
 Available, \\ \vspace{-0.05in} Upon Request.}
  
\end{minipage}
\hfill
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.3in}
  \flushright \footnotesize \addressblock \myphone \\
  {\scriptsize \texttt{\href{mailto:\myemail}{\myemail}}}
\end{minipage}

\medskip

%% Name
\noindent{\LARGE\scheader \textsc{michael steeves}}
\reversemarginpar

\bigskip

%% Skills
\marginhead{\sffamily skills}

\ind HPC; Infrastructure; Linux/Unix/OS X; AWS; SAN/NAS; Chef; R; C/C++; Python; Bash

\bigskip

%% Employment History
% \medskip
\marginhead{\sffamily employment}

\ind \textbf{Novartis Institute for BioMedical Research, Inc.} (July 2006 --- present)

\noindent\textit{Scientific Computing Group} (August 2010 -- present)
Global team supporting HPC environment for NIBR scientists
world-wide. Application and workflow support, new technology
evaluation for AWS cloud and Hadoop. Global application build
environment.

\ind \hspace{0.35in} \footnotesize 2013 Presenter at AWS
re:Invent\newline 2012 Global IT Innovation Award:
\textit{Software Engineering in the Cloud}.\newline 2012 Promotion to
Engineer/Senior Systems Specialist\newline 2011 Global IT
Innovation Award: \textit{Cloud-based High Throughut Docking}
\normalsize \vspace{0.05in}

\noindent\textit{Advanced Computing Services} (July 2006 -- August
2010) Site support for 1600 users, 400 servers and over 200 TB of
storage. IT lead in migrating Oracle RAC from NAS to SAN using OCFS2
and ASM on blade hardware. Lead for Nagios, Splunk, Cambridge business
continuity planning and global user account harmonization.

\ind\textbf{Tufts University} (Oct 2004 -- July 2006)

\noindent\textit{Unix Network Administrator} Member of 4 person team
responsible for infrastructure (e-mail, user accounts, web services,
50 servers, over 100 desktops, class/lab computing, storage/backup and
network) for ECE and CS departments.

\ind \textbf{Vertex Pharmaceuticals} (2001 -- Oct 2004)

\noindent\textit{Senior Unix System Administrator} Responsible for
Unix infrastructure (scientific servers/workstations, FDA-regulated
servers, e-mail infrastructure and 50-node Linux parallel compute
cluster), SAN and NAS storage.

\ind \textbf{GTE Internetworking/Genuity} (July 1999 - 2001)

\noindent\textit{Unix System Administrator} Responsible for a dozen
servers and over 150 desktops for several engineering departments,
including e-mail and user accounts.

\ind \textbf{Applix, Inc.} (March 1996 -- July 1999)

\noindent\textit{System and Network Engineer} (November 1998 -- July
1999) Responsible for heterogeneous Unix server and workstation
environment, LAN/WAN network, e-mail and PBX/Meridian Mail for
corporate headquarters and internal support for networks, phone
system, servers and Applixware and remote assistance to European
offices.

\noindent\textit{Customer Support Engineer} (March 1996 -- November
1998)

\bigskip

%% Education

\marginhead{\sffamily {{\vskip -0.23em} education}}

\ind Master of Science --- Bioinformatics, Brandeis University, February 2014

\ind Bachelor of Science --- Mathematics, University of Massachusetts at Lowell, 1997

\end{document}
